EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems

### 2025-05-02 03_edipack2.tex
Updated draft. * added a section of parse_Umatrix (to be written) * drafting attractive HM, figure loaded.

@@

\subsection{The quantum impurity problem}\label{sSecQIM}
We consider a general quantum impurity problem defined by the
following Hamiltonian:
$$
\hat{H} = \hat{H}_{imp} + \hat{H}_{bath} + \hat{H}_{hyb} + \hat{H}_{ph} + \hat{H}_{e-ph}
$$
which describes a  multi-orbital interacting quantum
impurity coupled to an electronic bath and to local, i.e. Holstein,
phonons. We assuming for the moment that no particular symmetry
holds. The impurity part of the Hamiltonian reads: 
\begin{equation}\label{Himp}
  \begin{split}
    \hat{H}_{imp} & = \hat{H}^0_{imp} + \hat{H}^{int}_{imp}\\
    \hat{H}^0_{imp} & =
    \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}d_{\b\sigma'}\\
    %
    \hat{H}^{int}_{imp} &=U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}\\
    &{\phantom =}- J_X\sum_{\a\neq
      \b}d^{+}_{\a\uparrow}d_{\a\downarrow}d^{+}_{\b\downarrow}d_{\b\uparrow}+J_P\sum_{\a
      \neq
      \b}d^{+}_{\a\uparrow}d^{+}_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow}\\
    % 
\end{split}
\end{equation}

@@

@@

>>>>

\documentclass[edipack2.tex]{subfiles}
\begin{document}

@@

\subsection{The quantum impurity problem}\label{sSecQIM}
We consider a general quantum impurity problem defined by the
following Hamiltonian:
$$
\hat{H} = \hat{H}_{imp} + \hat{H}_{bath} + \hat{H}_{hyb} + \hat{H}_{ph} + \hat{H}_{e-ph}
$$
which describes a  multi-orbital interacting quantum
impurity coupled to an electronic bath and to local, i.e. Holstein,
phonons. 
\begin{equation}\label{Himp}
  \begin{split}
    \hat{H}_{imp} & = \hat{H}^0_{imp} + \hat{H}^{int}_{imp}\\
    \hat{H}^0_{imp} & =
    \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}d_{\b\sigma'}\\
\end{split}
\end{equation}

We assume for the moment that no particular symmetry
holds. The impurity part of the Hamiltonian can, in principle, consist of any set of
two-body quantum operators of the form $U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}$.

A set of such operators is the celebrated Hubbard-Kanamori Hamiltonian:

\begin{equation}\label{Hint}
  \begin{split}
    \hat{H}^{int}_{imp} &=U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}\\
    &{\phantom =}- J_X\sum_{\a\neq
      \b}d^{+}_{\a\uparrow}d_{\a\downarrow}d^{+}_{\b\downarrow}d_{\b\uparrow}+J_P\sum_{\a
      \neq
      \b}d^{+}_{\a\uparrow}d^{+}_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow}\\
\end{split}
\end{equation}

@@

\subsection{Interaction setup}
\NAME offers two distinct ways to setup the interaction term in \equ{Himp}. 
The Hubbard-Kanamori interaction \equ{Hint} is supported natively, via the user-accessible
variables {\tt ULOC}$=U$, {\tt UST}$=U^{'}$, {\tt JH}$=J$, {\tt JX}$=J_{x}$ and {\tt JP
}$=J_{p}$.These parameters can be specified in the input file, and they will be read and 
set if the flag {\tt ED\_USE\_KANAMORI} is set to {\tt T}. This is the default option.
If the interaction Hamiltonian is provided via {\tt ED\_USE\_KANAMORI}, {\tt NORB} is limited to a maximum of {\tt 5}.

Alternatively, the list of two-body operators can be provided by the user in a properly
formatted text file, the name of which is specified in the {\tt UMATRIX\_FILE} input variable. The file has to have the suffix {\tt \\.restart}.
Such file needs to be formatted in the following way

\begin{lstlisting}[style=mybash]
NORB BANDS
i1 j1 k1 l1 U_i1j1k1l1
i2 j2 k2 l2 U_i2j2k2l2
...
\end{lstlisting}

where {\tt NORB} is the numer of orbitals. Empty lines and lines starting with {\tt \#, \%, !} are ignored. Notice the swapped indices in the coefficient with respect to the standard 2-body operator formulation $U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}$. To enable reading an interaction matrix file, the flag {\tt ED\_READ\_UMATRIX} needs to be set in the input file. {\tt ED\_READ\_UMATRIX} and {\tt ED\_USE\_KANAMORI} are mutually exclusive, but they can be both false.
Before the impurity problem is solved, the used can also provide interaction terms in the program or script. Extensive documentation is available at (\textcolor{red}{how should we do this?})
All the interaction operators used in each call of the solver are listed and written in an output file. called {\tt UMATRIX\_FILE.used}.

@@

\end{document}
